\tb{Place of Residence and Political Attitudes in Democracies Worldwide \\ {\large Online Appendix C -- Margins Plots} }

### 2019-02-13 F18Version/Final Paper/PaperJLin.tex
Moved to New Folder

Elections in Canada follow a similar pattern to the trends noted in the United States. While it is a younger democratic regime in comparison and has representative that are elected via a proportional representation system, research in Canadian elections starting in 2003 \citep{walks_place_2004} suggest that the divide between place of residence is present and exacerbated by party polarization in the political system. Canada's New Democratic Party selects candidates that prioritize the needs of cities, pushing voters in the suburbs and rural areas to support a more conservative, right-wing option. A time series of Canadian elections from 1945 to present also confirms this drift and divide between voters based on their place of residence \citep{walks_city-suburban_2005}.

@@

In general, the possibilities of social interactions between people in a specific vicinity matters in how they will form their political attitudes. Early research in this field \citep{glenn_rural-urban_1967} shows that rural residents are less trusting of their neighbors than their urban counterparts.  In a more recent study using 2000 Census data in the United States, the research suggests that diversity is a great factor influencing liberal views, or lack thereof \citep{williamson_sprawl_2008}. When people are in places where diversity is vibrant, they are more likely to be open to newer experiences. Yet, this is most likely, in modern times, an occurrence of the urban centers and less so once one moves to the margins of geographic space in society. Therefore, space matters in the opportunities for attitude development because it facilitates one's exposure to diversity and opens the door to possibilities. Yet, at the same time, the state of development of the country on it's path to democracy, along with the political participation of the individual residents, also contribute to the connections between place of residence and political ideology.

@@

Now that we've analyzed the distribution of respondents by polity and the elections that the country is having in the studied election cycle, it is also beneficial to note some of the macro trends that are present which can help categorize the countries and take their variations into account in the analysis. As we will see later, I use the CSES labels for democracy but also include several variables to check the definition of democracy to be as \cite{diamond2004overview} categorizes it's key characteristics to be regimes that grant citizens individual freedoms, equality before the law and feature government responsiveness.

@@

Figure \ref{figure2} shows a graphical display of the countries represented in Module IV of the CSES sorted by their level of democracy and regime age. As the graph suggests, most of the countries represented in this study are very free. Yet, when it comes to the time that the electoral democracy has been around, most reside under the 50 year mark but it largely centers around and below 25 years. For a better breakdown of the exact values of each country's regime age and level of democracy, Table \ref{table101} in Appendix \ref{AppendixC} shows this data broken down more specifically, adding the consideration of the regime's electoral formula. From what this figure can show us, it is important to note some extreme values on both variables. Turkey's 2015 election stands out on Figure \ref{figure2} because it is the least democratic of the group. Additionally, it is also interesting to note the longest standing democracies such as the United States, Switzerland, Australia, Canada and New Zealand. These countries are those where there are most prior research given the country's openness to gathering of data from its citizens and the people's abilities to express their desires freely. The countries that center around eight and nine on the democracy scale that have democracies that are younger than 50 years will be the most interesting to consider given limitations in the existing literature that is available for these places.

@@

The \e{Place Matters} hypothesis suggests that there is a direct relationship between place of residence and political ideology no matter where an individual lives in this world. Therefore, this hypothesis assumes that, broadly speaking, individuals who live in a rural area will be more conservative than those who live in a small town or urban center. In this case, political ideology, as we will also see later, is operationalized by the respondent's self-placement on the ideology spectrum. Therefore, this is based on their own views on how liberal or conservative they are. While this is helpful to understand how place of residence influences political ideology, it would be even more helpful to introduce a second hypothesis that looks at objective support for policies which can show where a person lies on the political spectrum.

@@

Finally, I include the electoral formula as a means of understanding how the system of representation influences the relationship between the core variables used in this paper. A regime's electoral formula is the way in which citizens select their representatives and the mechanisms in which votes are tallied. It is unclear whether the electoral formula influences political discourse and attitude formation. however, past research suggests that this factor does not matter in the ways that place of residence will influence a person's political preference \cite{barkan_space_2006}. For the \e{Electoral Formula} hypothesis, I hypothesize that if individuals had to fight for representation in a winner take all system, personal factors such as place of residence will be more salient than if all interests were more fairly represented in a proportional system. Each of these components are then tied together to understand how idiosyncrasies of a polity lead to the difference between place of residence and political ideology as explored in the \e{Self-Identified Ideology} and the \e{Issue Stances} hypotheses.

@@

Each individual's country of residence is also classified based on the year of the election, level of democracy during the election year,  age of the current governing regime in the country at the time of the election, and the type of electoral formula employed by the governing body to determine winners of seats in government. The level of democracy is characterized by how free the polity is at the time of the election. This measure was gathered from the generators of the Polity IV project and reflects freedom from a -10 to 10 scale with -10 being the most autocratic and 10 being the most democratic. The age of the current governing regime suggests how long the current system has been in power. The larger value suggests that the current system in government has been established for a longer period of time and is therefore more stable. Finally, the type of electoral formula describes how government official win office based on their total vote share. Contestants may win via majoritarian, proportional or mixed system.

@@

To understand where individuals see their own political values, the dependent variable reflects their self-identified ideology, a variable coded by the CSES that ranges from 0 to 10 with 0 being the most left leaning and 10 as the most right leaning ideological stance.. Since this can be rather subjective, I also created a liberalism scale that reflects individual values on government spending with a more liberal vision being those who value spending for social benefits and a more conservative view for those who do not with for such spending or for those who wish to spend more to boost defense as a means to secure their country's identity and values. (See Appendix \ref{AppendixB} for a more detailed description of this scale creation) This 9-point scale was generated from questions relating to public expenditure used in the survey. Topics for these questions include health, education, unemployment benefits, defense, old age pensions, business and industry investments, police and law enforcement and welfare benefits. Additionally, I add a value of economic equality to the measure as a means of understanding how each person values equality as part of their ideological outlook. This scale ranges from 0 to 9, with 9 being the most conservative and 0 being the most liberal. In the broadest context, respondents who score at the extreme ends of the scale are seen to be most conservative or liberal in terms of their outlook on spending, which can speak to their views on social values given their willingness to allocate government money to these groups.

@@

When the analysis is broken down by the countries themselves, we see a clearer patterns between place of residence and political attitudes of the respondents to the CSES survey. Each country is displayed and analyzed with their regional neighbors. Additionally, these trends are discussed in context of some key macro variables present for each polity that is displayed in Figure \ref{figure2} and Appendix \ref{AppendixC}. By conducting the analyses in this manner, we can also see if there is a neighborhood effect, such that countries that are located near one another are similar in democratic and demographic ideological arenas.

@@

In Western Europe, the results confirm the \e{Self-Identified Ideology} hypothesis for France, but not Germand. In Table \ref{table5}, we can see that differences between France and Germany lie in the distinction between urban residents compared to rural residents. While both countries see urban residents lean left on the self-identified scale, France is more statistically significant in their .64 point jump to the left, which is relatively large for a 10 point scale. Geographically, Germany is considered more in Central Europe; however, their political activity makes them a worthwhile comparison to Western Europe.

@@

When we turn to Western Europe, we see a similar trend that Central and Latin America has with the results between the two dependent variables. Under the \e{Self-Identified Ideology} hypothesis model, France's citizens showed that living in a more urban place led to greater feelings of left-leaning sentiment, but the general trends under the |e{Issue Stances} hypothesis model does not show this. Rather, there is a movement towards the right, albeit not as significant. These patterns are also seen in Central Europe. with the exception of Czech Republic. While the country moved towards the right in the previous model, there was no indication of a real difference between places of residence and political attitudes. However, their shift under the present model suggests that when it comes to objective issue stances, there is a difference between urban and rural residents. The suburban residents of Poland also show that place matters between rural villages and suburbia when is comes to attitudes towards government spending such that suburban residents are more liberal, but this effect is not seen in the urban centers.

@@

In Southwestern Europe, Greece confirms the \e{Issue Stances} hypothesis such that the urban residents are more likely than chance to say that they are more open to government spending than rural residents. This pattern is observed in the oppesite direction for Montenegro and Romania in 2012. Yet, the same cannot be said for Latvia in their 2014 election, the sole case here from Eastern Europe.

@@

As we can see from these analyses relating to issue stances, place of residence matters but, like the results of the \e{Self-Identified Ideology} hypothesis results, these vary widely across differences in level of democracy, regime age and electoral formula.

@@

%Self Placement and Liberalism Column Changed
\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}
	\\
	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &.1301*&-.0275 \\
	&(..0736)&(.0269) \\
	Suburban& .0884& -.0741** \\
	&(..0976)& (.0347) \\
	Urban&.1484** & .0995*** \\
	&(..0751) & (.0266) \\
	\e{Democracy}& .1178***& .0030***\\
	&(..0357) & (.0120)\\
	\e{Regime Age} & -.0037** & .0035***\\
	&(..0016) & (.0005)\\
	\e{Electoral Formula}&-.0518& .0888***\\
	&(..0484) & (.0167) \\
	\e{Freedom House}& -.8108*** &-.0593*** \\
	&(.1065) & (.0340)  \\
	\e{Corruption Perception}&.0226***&.0148*** \\
	&(.0044)& (.0014)  \\
	\hline
	Constant& 7.928*** & 2.1065*** \\
	&(.4323) & (.1439)\\
	N&10,122 & 9,292 \\
	$R^2$&0.0509& 0.1113 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

@@

A model that considers the interaction between a person's place of residence and their country's level of democracy suggests that the level of democracy only differs slightly between places such that there is almost no effect between your country's level of democracy and where you live that will make a noticeable difference on your personal political ideology nor your feelings towards government spending.

@@

For this section, we consider Electoral formula. Since there are only 3 categories that any country can select, it makes direct comparison more straightforward. Unlike the previous two discussions, this variable is not continuous, thereby making interactions not as suitable.

\begin{table}[h!]
	\centering
	\caption{\tb{Ideology In Each Electoral Formula}}
	\begin{tabulary}{\linewidth}{l c c c}
		\\
		\hline
		\tb{Place of Residence}&\tb{Majoritarian}&\tb{Proportional} &\tb{Mixed} \\
		\hline
		Small Town&-.2413 &.3437*** &.0425 \\
		&(.1583)&(.0982) &(.1377) \\
		Suburban&-.0981 &.2715**&.4923**  \\ 
		&(.2307) &(.1174) &(.2124) \\
		Urban&-.3787* &.1999** &.5009*** \\
		&(.1995) &(.0981) &(.1298) \\
		Constant& 1.776*** &5.3337***&5.9321*** \\
		&(.5730) &(.2616) &(.3651) \\
		N&1,440&6,057 &3,043\\
		$R^2$&0.1375&0.0549&0.0221 \\
		\hline 
	\end{tabulary} 
\\ 
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table16}
\end{table}

Table \ref{table16} shows the relationship of place of residence in countries grouped by their electoral formula. By the differences in the results, we can see that the electoral formula matters in the relationship between place of residence and political attitudes.

Majoritarian elections are defined by first-past-the-post result tabulations where the candidate with the most votes is tapped as the winner of the race. With this campaign method, there is space of candidates to appeal to certain constituencies strategically to gain the most votes for themselves. In theory, a large representative body should serve different interests, but reality is hard to match expectations. Therefore, candidates and voters alike must push for their own interests to dominate, making a polarized electorate more likely on the lines of differing interest \cite{abramowitz-2010}. The results confirms this expectation. Individuals living in small towns, suburban and urban areas are more likely to lean left than their rural counterparts. However, from the results shows in Table \ref{table15}, only urban residents have statistical significance compared to their rural counterparts, but it is over a third of a point to the left, making that a moderate influence. Despite the aggregated statistical significance, it is also important to note that this pattern is not present for all majoritarian systems when broken down. The only country where this same pattern is seen is in France. Other majoritarian countries may see a move in this general direction, but not to the extent of statistical significance.

Proportional representation occurs when parties are able to allocate votes in ratio to the number of votes that they receive. Therefore, it becomes more likely that different interests are represented in practice and that minority parties will have a chance in policy-making. Yet the results suggest that there is a rural-urban divide among the respondents, and this effect is present in all areas of residence studied in this analysis. From the results, we see that there is a trend towards conservatism, even if it is more pronounced in small towns compared to rural areas than in urban centers compared to rural areas. Yet, while the aggregate tells this picture, there are also proportional systems that confirm the |e{Self-Identified Ideology} hypothesis, namely Greece in 2012 and South Africa. There are proportional systems that may move in the direction of the aggregate but the observations may occur due to chance.

Finally, a mixed representation system has combinations of the aforementioned systems. When aggregated, there are differences between place of residence and political attitudes. Much like the results in a proportional system, the responses for urban residents are over a half a point to the right, which is a relatively significant amount for countries in this system. This trend goes against the observations of Mexico in their 2015 electon, even if it confirms the patterns of Romania in 2012.

@@

As mentioned earlier in this paper, Freedom House Ratings and the Corruption Perception Index score for each country was included in this analysis model to control and understand how each country meets the criteria for a free and fair democracy as defined by \cite{diamond2004overview} in his paper. To understand the freedom, equality and responsiveness principles, I include these variables both as controls and as independent variables to see how they themselves would interact with place of residence to influence one's political ideology and attitudes towards government spending.

@@

Taken together, the analyses in this section suggest that when each of these macro variables are alone, they may produce effects not observed by chance, but they can also produce some interactive effects with the place of residence variable. The lack of results in this section suggests that not one polity defining variable can work to produce significance in its influence of the relationship between place and political ideology. This is an effect that can lead to future research to understand how the variables cooperate to create effects. While I was not able to gain an understanding of overall cooperative effects of the five macro variables, the regressions for each individual country suggests that there are still variations between the polities beyond these five that can determine whether there is a place difference for political ideology and issue attitudes.

@@

Finally, in Hypothesis 3, we examine the macro variables that are part of defining major democratic aspects of each country. We find that the \e{Polity Differences} hypothesis holds true when self-placement on the ideological spectrum is the dependent variable. When these factors are included in a model along with Freedom House Rating and Corruption Perception Index, the results suggest that these variables are contributing factors to how the worldwide trends operate in the ability for people in different places of residence to express their political attitudes. However, individually, there are limited differences between levels in each factor and its role in the relationship between the variables. We have some reason to suggest that these factors are cooperating in each country to influence the trends of influence between place and political attitudes, yet this would have to be proven through future research.

@@

	1. Strongly agree \\
	2. Somewhat agree 
	3. Neither agree nor disagree \\
	4. Somewhat disagree \\
	5. Strongly disagree \\ 
	7. Volunteered: Refused \\
	8. Volunteered: Don't Know \\
	9. Missing
\end{quote}

>>>>

Elections in Canada follow a similar pattern to the trends noted in the United States. While it is a younger democratic regime in comparison and has representative that are elected via a proportional representation system, research in Canadian elections starting in 2003 suggest that the divide between place of residence is present and exacerbated by party polarization in the political system \citep{walks_place_2004}. Canada's New Democratic Party selects candidates that prioritize the needs of cities, pushing voters in the suburbs and rural areas to support a more conservative, right-wing option. A time series of Canadian elections from 1945 to present also confirms this drift and divide between voters based on their place of residence \citep{walks_city-suburban_2005}.

@@

In general, the possibilities of social interactions between people in a specific vicinity matters in how they will form their political attitudes. Early research in this field \citep{glenn_rural-urban_1967} shows that rural residents are less trusting of their neighbors than their urban counterparts.  In a more recent study using 2000 Census data in the United States, the research suggests that diversity is a great factor influencing liberal views, or lack thereof \citep{williamson_sprawl_2008}. When people are in places where diversity is vibrant, they are more likely to be open to newer experiences. Yet, this is most likely, in modern times, an occurrence of the urban centers and less so once one moves to the margins of geographic space in society. Therefore, space matters in the opportunities for attitude development because it facilitates one's exposure to diversity and opens the door to possibilities. Yet, at the same time, the state of development of the country on it's path to democracy, along with the political participation of the individual residents, also contribute to the connections between place of residence and political ideology. Therefore, the connection between place and political attitudes rests both in the upbringing of the individual, their opportunities, and the development factors that surround the country that they live in.

@@

In addition to the distribution of residents, it is also beneficial to note some of the macro trends that are present which can help categorize the countries and take their variations into account in the analysis. As we will see later, I use the CSES variable for democracy but also include several other factors to check the definition of democracy to be as close to how \cite{diamond2004overview} categorizes its key characteristics -- regimes that grant citizens individual freedoms, equality before the law and feature government responsiveness.

@@

Figure \ref{figure2} shows a graphical display of the countries represented in Module IV of the CSES sorted by their level of democracy and regime age. As the graph suggests, most of the countries represented in this study are very free. Yet, when it comes to the time that the electoral democracy has been around, most reside under the 50 year mark but it largely centers around and below 25 years. Table \ref{table101} in Appendix \ref{AppendixC} shows this data broken down more specifically, adding the consideration of the regime's electoral formula.

From what this figure can show us, it is important to note some extreme values on both variables. Turkey's 2015 election stands out on Figure \ref{figure2} because it is the least democratic of the group. Additionally, it is also interesting to note the longest standing democracies such as the United States, Switzerland, Australia, Canada and New Zealand. These countries are those where there are most prior research given the country's openness to gathering of data from its citizens and the people's abilities to express their desires freely. The countries that center around eight and nine on the democracy scale that have democracies that are younger than 50 years will be the most interesting to consider given limitations in the existing literature that is available for these places.

@@

The \e{Self-Identified Ideology} hypothesis suggests that there is a direct relationship between place of residence and political ideology no matter where an individual lives in this world. Therefore, this hypothesis assumes that, broadly speaking, individuals who live in a rural area will be more conservative than those who live in a small town or urban center. In this case, political ideology, as we will also see later, is operationalized by the respondent's self-placement on the ideology spectrum. Therefore, this is based on their own views on how liberal or conservative they are. While this is helpful to understand how place of residence influences political ideology, it would be even more helpful to introduce a second hypothesis that looks at objective support for policies which can show where a person lies on the political spectrum.

@@

Finally, I include the electoral formula as a means of understanding how the system of representation influences the relationship between the core variables used in this paper. A regime's electoral formula is the way in which citizens select their representatives and the mechanisms in which votes are tallied. It is unclear whether the electoral formula influences political discourse and attitude formation. however, past research suggests that this factor does not matter in the ways that place of residence will influence a person's political preference \citep{barkan_space_2006}. For the \e{Electoral Formula} hypothesis, I hypothesize that if individuals had to fight for representation in a winner take all system, personal factors such as place of residence will be more salient than if all interests were more fairly represented in a proportional system. Each of these components are then tied together to understand how idiosyncrasies of a polity lead to the difference between place of residence and political ideology as explored in the \e{Self-Identified Ideology} and the \e{Issue Stances} hypotheses.

@@

Each individual's country of residence is also classified based on the year of the election, level of democracy during the election year,  age of the current governing regime in the country at the time of the election, and the type of electoral formula employed by the governing body to determine winners of seats in government. The level of democracy is characterized by the functions of the ability for people to govern at the time of the election. This measure was gathered from the generators of the Polity IV project and reflects democratization from a -10 to 10 scale with -10 being the most autocratic and 10 being the most democratic. The definition of democracy used in this measure largely follow the \cite{linz1996problems} conceptualization as the ability for the regime to hold free, fair, open and competitive elections to select leaders on the central government. The age of the current governing regime suggests how long the current system has been in power. The larger value suggests that the current system in government has been established for a longer period of time and is therefore more stable. Finally, the type of electoral formula describes how government official win office based on their total vote share. Contestants may win via majoritarian, proportional or mixed system.

@@

To understand where individuals see their own political values, the dependent variable reflects their self-identified ideology, a variable coded by the CSES that ranges from 0 to 10 with 0 being the most left leaning and 10 as the most right leaning ideological stance. Since this can be rather subjective, I also created a liberalism/issue stances scale that reflects individual values on government spending with a more liberal vision being those who value spending for social benefits and a more conservative view for those who do not with for such spending or for those who wish to spend more to boost defense as a means to secure their country's identity and values. (See Appendix \ref{AppendixB} for a more detailed description of this scale creation) This 9-point scale was generated from questions relating to public expenditure used in the survey. Topics for these questions include health, education, unemployment benefits, defense, old age pensions, business and industry investments, police and law enforcement and welfare benefits. Additionally, I add a value of economic equality to the measure as a means of understanding how each person values equality as part of their ideological outlook. This scale ranges from 0 to 9, with 9 being the most conservative and 0 being the most liberal. In the broadest context, respondents who score at the extreme ends of the scale are seen to be most conservative or liberal in terms of their outlook on spending, which can speak to their views on social values given their willingness to allocate government money to these groups.

@@

When the analysis is broken down by the countries themselves, we see a clearer patterns between place of residence and political attitudes of the respondents to the CSES survey. Each country is displayed and analyzed with their regional neighbors. Additionally, these trends are discussed in context of some key macro variables present for each polity that is displayed in Figure \ref{figure2} and Appendix \ref{AppendixC}. By conducting the analyses in this manner, we can also see if there is a neighborhood effect, such that countries that are located near one another are similar in democratic and demographic ideological arenas \citep{brinks2006diffusion}.

@@

In Western Europe, the results confirm the \e{Self-Identified Ideology} hypothesis for France, but not Germany. In Table \ref{table5}, we can see that differences between France and Germany lie in the distinction between urban residents compared to rural residents. While both countries see urban residents lean left on the self-identified scale, France is more statistically significant in their .64 point jump to the left, which is relatively large for a 10 point scale. Geographically, Germany is considered more in Central Europe; however, their political activity makes them a worthwhile comparison to Western Europe.

@@

When we turn to Western Europe, we see a similar trend that Central and Latin America has with the results between the two dependent variables. Under the \e{Self-Identified Ideology} hypothesis model, France's citizens showed that living in a more urban place led to greater feelings of left-leaning sentiment, but the general trends under the \e{Issue Stances} hypothesis model does not show this. Rather, there is a movement towards the right, albeit not as significant. These patterns are also seen in Central Europe. with the exception of Czech Republic. While the country moved towards the right in the previous model, there was no indication of a real difference between places of residence and political attitudes. However, their shift under the present model suggests that when it comes to objective issue stances, there is a difference between urban and rural residents. The suburban residents of Poland also show that place matters between rural villages and suburbia when is comes to attitudes towards government spending such that suburban residents are more liberal, but this effect is not seen in the urban centers.

@@

In Southwestern Europe, Greece confirms the \e{Issue Stances} hypothesis such that the urban residents are more likely than chance to say that they are more open to government spending than rural residents. This pattern is observed in the opposite direction for Montenegro and Romania in 2012. Yet, the same cannot be said for Latvia in their 2014 election, the sole case here from Eastern Europe.

@@

As we can see from these analyses relating to issue stances, place of residence matters but, like the results of the \e{Self-Identified Ideology} hypothesis, these vary widely across differences in level of democracy, regime age and electoral formula.

@@

%Self Placement and Liberalism Column Changed
\begin{table}[h!]
	\centering
	%\def\arraystretch{1.5}
	\caption{\tb{All Macro Variables - General Trends}}
	\begin{tabulary}{\linewidth}{l c c}

	\hline
	\tb{Variable}&\tb{Self-Placement}&\tb{Liberalism} \\
	\hline
	\e{Place of Residence} & & \\
	Small Town &.1301*&-.0275 \\
	&(..0736)&(.0269) \\
	Suburban& .0884& -.0741** \\
	&(..0976)& (.0347) \\
	Urban&.1484** & .0995*** \\
	&(..0751) & (.0266) \\
	\e{Democracy}& .1178***& .0030***\\
	&(..0357) & (.0120)\\
	\e{Regime Age} & -.0037** & .0035***\\
	&(..0016) & (.0005)\\
	\e{Electoral Formula}&-.0518& .0888***\\
	&(..0484) & (.0167) \\
	\e{Freedom House}& -.8108*** &-.0593*** \\
	&(.1065) & (.0340)  \\
	\e{Corruption Perception}&.0226***&.0148*** \\
	&(.0044)& (.0014)  \\
	\hline
	Constant& 7.928*** & 2.1065*** \\
	&(.4323) & (.1439)\\
	N&10,122 & 9,292 \\
	$R^2$&0.0509& 0.1113 \\
	\hline
	\end{tabulary}
	\\
\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
\e{Reference:} A rural place of residence serves as the baseline for comparison
\label{table15}
\end{table}

@@

A model that considers the interaction between a person's place of residence and their country's level of democracy suggests that the level of democracy, alone, only differs slightly between places such that there is almost no effect between your country's level of democracy and where you live that will make a noticeable difference on your personal political ideology nor your feelings towards government spending.

@@

%For this section, we consider Electoral formula. Since there are only 3 categories that any country can select, it makes direct comparison more straightforward. Unlike the previous two discussions, this variable is not continuous, thereby making interactions not as suitable.

%\begin{table}[h!]
%	\centering
%	\caption{\tb{Ideology In Each Electoral Formula}}
%	\begin{tabulary}{\linewidth}{l c c c}
%		\hline
%		\tb{Place of Residence}&\tb{Majoritarian}&\tb{Proportional} &\tb{Mixed} \\
%		\hline
%		Small Town&-.2413 &.3437*** &.0425 \\
%		&(.1583)&(.0982) &(.1377) \\
%		Suburban&-.0981 &.2715**&.4923**  \\ 
%		&(.2307) &(.1174) &(.2124) \\
%		Urban&-.3787* &.1999** &.5009*** \\
%		&(.1995) &(.0981) &(.1298) \\
%		Constant& 1.776*** &5.3337***&5.9321*** \\
%		&(.5730) &(.2616) &(.3651) \\
%		N&1,440&6,057 &3,043\\
%		$R^2$&0.1375&0.0549&0.0221 \\
%		\hline 
%	\end{tabulary} 
%\\ 
%\e{Notes:} *p$<$.1, **p$<$.05. ***p$<$.01 \\
%\e{Reference:} A rural place of residence serves as the baseline for comparison
%\label{table16}
%\end{table}

%Table \ref{table16} shows the relationship of place of residence in countries grouped by their electoral formula. By the differences in the results, we can see that the electoral formula matters in the relationship between place of residence and political attitudes.

Differences in the method of election can lead to differences in campaign strategies and voting styles. Therefore, the political ideologies of individuals can be based in the electoral system and political culture established and developed during a country's transition to democracy.

Majoritarian elections are defined by first-past-the-post result tabulations where the candidate with the most votes is tapped as the winner of the race. With this campaign method, there is space of candidates to appeal to certain constituencies strategically to gain the most votes for themselves. In theory, a large representative body should serve different interests, but reality is hard to match expectations. Therefore, candidates and voters alike must push for their own interests to dominate, making a polarized electorate more likely on the lines of differing interest \cite{abramowitz-2010}. The results confirms this expectation. Individuals living in small towns, suburban and urban areas are more likely to lean left than their rural counterparts. However, only urban residents have statistical significance compared to their rural counterparts, but it is over a third of a point to the left, making that a moderate influence. Despite the aggregated statistical significance, it is also important to note that this pattern is not present for all majoritarian systems when broken down. The only country where this same pattern is seen is in France. Other majoritarian countries may see a move in this general direction, but not to the extent of statistical significance.

Proportional representation occurs when parties are able to allocate votes in ratio to the number of votes that they receive. Therefore, it becomes more likely that different interests are represented in practice and that minority parties will have a chance in policy-making. Yet the results suggest that there is a mild rural-urban divide among the respondents, and this effect is present in all areas of residence studied in this analysis. From the results, we see that there is a trend towards conservatism, even if it is more pronounced in small towns compared to rural areas than in urban centers compared to rural areas. Yet, while the aggregate tells this picture, there are also proportional systems that confirm the \e{Self-Identified Ideology} hypothesis, namely Greece in 2012 and South Africa. There are proportional systems that may move in the direction of the aggregate but the observations may occur due to chance.

Finally, a mixed representation system has combinations of the aforementioned systems. When aggregated, there are differences between place of residence and political attitudes. Much like the results in a proportional system, the responses for urban residents are over a half a point to the right, which is a relatively significant amount for countries in this system. This trend goes against the observations of Mexico in their 2015 election, even if it confirms the patterns of Romania in 2012.

@@

As mentioned earlier in this paper, Freedom House Ratings and the Corruption Perception Index score for each country was included in this analysis model to control and understand how each country meets the criteria for a free and fair democracy as defined by \cite{diamond2004overview}. To understand the freedom, equality and responsiveness principles, I include these variables both as controls and as independent variables to see how they themselves would interact with place of residence to influence one's political ideology and attitudes towards government spending.

@@

Taken together, the analyses in this section suggest that when each of these macro variables are alone, they may produce effects not observed by chance, but they can also produce some interactive effects with the place of residence variable. The null results in this section suggests that not one polity defining variable can work to produce significance in its influence of the relationship between place and political ideology. This is an effect that can lead to future research to understand how the variables cooperate to create effects. While I was not able to gain an understanding of overall cooperative effects of the five macro variables, the regressions for each individual country suggests that there are still variations between the polities beyond these five that can determine whether there is a place difference for political ideology and issue attitudes.

@@

Finally, in Hypothesis 3, we examine the macro variables that are part of defining major democratic aspects of each country. We find that the \e{Polity Differences} hypothesis holds, but to a rather limited extent for both dependent variables. When these factors are included in a model along with Freedom House Rating and Corruption Perception Index, the results suggest that these variables are contributing factors to how the worldwide trends operate in the ability for people in different places of residence to express their political attitudes. However, individually, there are limited differences between levels in each factor and its role in the relationship between the variables. We have some reason to suggest that these factors are cooperating in each country to influence the trends of influence between place and political attitudes, yet this would have to be proven through future research.

@@

	1. Strongly agree \\
	2. Somewhat agree \\
	3. Neither agree nor disagree \\
	4. Somewhat disagree \\
	5. Strongly disagree \\ 
	7. Volunteered: Refused \\
	8. Volunteered: Don't Know \\
	9. Missing
\end{quote}

### 2019-02-13 F18Version/Online Appendices/Appendix C.tex
Moved to New Folder

\usepackage{fullpage} %full page typesetting
\usepackage{setspace} %allows for non-singlespacing
\usepackage{graphicx} %graphics capabilities
\usepackage{latexsym} %extra symbols
\usepackage{rotating} %rotation for figures
\usepackage{longtable} %tables that fill more than a single page
%\usepackage{hyperref} %hypertext links in the document
\usepackage{natbib} %better bibliographies
\usepackage{authblk} %author and affiliation in opening
\usepackage{mathpazo} %use palatino font, rather than times
\usepackage{appendix}
\usepackage{lscape}
\usepackage{tabulary}
\usepackage[nottoc]{tocbibind}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=cyan]{hyperref}
\usepackage{ifthen}
\usepackage{float}
\usepackage{subcaption}
\usepackage{mwe}
\usepackage{caption}

@@

>>>>

\usepackage{fullpage} %full page typesetting
\usepackage{setspace} %allows for non-singlespacing
\usepackage{graphicx} %graphics capabilities
\usepackage{latexsym} %extra symbols
\usepackage{rotating} %rotation for figures
\usepackage{longtable} %tables that fill more than a single page
%\usepackage{hyperref} %hypertext links in the document
\usepackage{natbib} %better bibliographies
\usepackage{authblk} %author and affiliation in opening
\usepackage{mathpazo} %use palatino font, rather than times
\usepackage{appendix}
\usepackage{lscape}
\usepackage{tabulary}
\usepackage[nottoc]{tocbibind}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=cyan]{hyperref}
\usepackage{ifthen}
\usepackage{float}
\usepackage{subcaption}
\usepackage{mwe}
\usepackage{caption}
\usepackage{listings}
\lstset{
	basicstyle=\small\ttfamily,
	columns=flexible,
	breaklines=true
}

@@

\begin{lstlisting}
*Interaction with Place and Democracy
reg ideology i.place##i.democracy regimeage electformula freedomhouse corrupt gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(democracy=(8(1)10))
marginsplot
graph export "IdeoPlaceDem.pdf", replace

reg liberalism i.place##i.democracy regimeage electformula freedomhouse corrupt gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(democracy=(8(1)10))
marginsplot
graph export "LibPlaceDem.pdf", replace

*Interaction with Place and Regime Age
reg ideology i.place##c.regimeage electformula democracy freedomhouse corrupt gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(regimeage=(0(25)200))
marginsplot
graph export "IdeoPlaceAge.pdf", replace

reg liberalism i.place##c.regimeage electformula democracy freedomhouse corrupt gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(regimeage=(0(25)200))
marginsplot
graph export "LibPlaceAge.pdf", replace

*Interaction with Place and Electoral Formula
reg ideology i.place##i.electformula regimeage democracy freedomhouse corrupt gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(electformula=(1 2 3))
marginsplot
graph export "IdeoPlaceFormula.pdf", replace

reg liberalism i.place##i.electrformula regimeage democracy freedomhouse corrupt gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(electofrmula=(1 2 3))
marginsplot
graph export "LibPlaceFormula.pdf", replace

*Interaction with Place and Freedom House Rating
reg ideology i.place##c.freedomhouse electformula regimeage democracy corrupt gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(freedomhouse=(4(.5)7))
marginsplot
graph export "IdeoPlaceFree.pdf", replace

reg liberalism i.place## c.freedomhouse electformula regimeage democracy corrupt gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(freedomhouse=(4(.5)7))
marginsplot
graph export "LibPlaceFree.pdf", replace

*Interaction with Place and Corruption
reg ideology i.place##c.corrupt freedomhouse electformula regimeage democracy gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(corrupt=(0(10)100))
marginsplot
graph export "IdeoPlaceCorrupt.pdf", replace

reg liberalism i.place##c.corrupt freedomhouse electformula regimeage democracy gender age ses education partyid close religion
rvfplot
margins, dydx(place) at(corrupt=(0(10)100))
marginsplot
graph export "LibPlaceCorrupt.pdf", replace
\end{lstlisting}
